### 2016-06-23 appendix.tex
Lets fix sec 6!!
aaaaa

\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT}}
\begin{proof}
For soundness, let $P$ be a pattern enumerated by SPARE, then $\forall o_1, o_2 \in P.O$ they belongs to the same star. As the enumerate algorithm only reduce the time sequences, $P.T \subset e(o_1,o_2)$. This indicates that, $\forall t \in P.T$, $t\in e(o_1,o_2)$. By the definition of star, $C_t(o_1) = C_t(o_2)$. Since $P.T$ conforms to $K,L,G$,  by the definition of GCMP, $P.T$ is a true pattern.
For completeness, let $P$ is a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} with $Sr_s$. 
First, based on the definition of star partition, every object in $P.O$ appears in $Sr_s$. Note that $P.T$ conforms to $K,L,G$, then $\forall O' \subseteq O$, the time sequence of $O'$ is a super set of a decomposable sequence. This indicates that any $O'$ would not be eliminated by any $\mathtt{sim}$ operations in Algorithm~\ref{algo:apriori_mining}.  Next, we prove in iterations $(1,\ldots,P.|O|-2)$, $P.O \subset U_i$, where $U_i$ is the forward closure. We prove by induction. When $i$ = 2, it obviously holds. If $P.O \subset U_i$ at iteration $i$, then any subset of $P.O$ with size $i+2$ are in the candidate set. In iteration $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$). This suggests that no subsets are removed by Line~\ref{code:output1}. Then, $P.O \subset U_{i+1}$ holds.  In summary, $P.O$ does not pruned by simplification and monotonicity and forward closure, therefore $P$ can be returned by SPARE.
%Next, observe that at each iteration $i$, candidates with size $i+2$ are generated. Then, $P.O$'s subset with size $i+2$ are always included in the candidate set at iteration $i$. This indicates that $O' \subset U$, thus any $O'$  would not be pruned by forward closure checking. Since none of the pruning operations removed $O'$, $P$ can be returned by SPARE.
%
%\begin{theorem}[Forward Closure Checking]
%\label{THM:SPM_FCC}
%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
%if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
%and directly output $FC_i$.
%\end{theorem}

>>>>

\subsection{Proof of Theorem~\ref{THM:SPM_CORRECT}}
\begin{proof}
For soundness, let $P$ be a pattern enumerated by SPARE. Since the enumerate algorithm only reduces the time sequences, for any two objects $o_1, o_2 \in P.O$, the edge $e(o_1,o_2)$ is a superset of $P.T$. By the definition of star, $\forall t \in T, C_t(o_1) = C_t(o_2)$. As $T$ is a valid sequence, by the definition of GCMP, $P$ is a true pattern.
For completeness, let $P$ is a true pattern. Let $s$ be the object with smallest ID in $P.O$. We prove that $P$ must be output by Algorithm~\ref{algo:apriori_mining} with input $Sr_s$. 
First, based on the definition of star, every object in $P.O$ appears in $Sr_s$. Since $P.T$ is decomposable, then $\forall O' \subseteq O$, the time sequence of $O'$ is a super set of a decomposable sequence. This indicates that $O'$ would not be eliminated by any $\mathtt{sim}$ operations in Algorithm~\ref{algo:apriori_mining}.  Next, we prove at every iteration \emph{level} $\leq |P.O|$, $P.O \subset O_u$, where $O_u$ is the forward closure. We prove by induction. When $level$ = 2, it obviously holds. If $P.O \subset O_u$ at \emph{level=$i$}, then any subset of $P.O$ with size $i$ are in the candidate set. In \emph{level} $i+1$, these subsets are able to grow to a bigger subset (in last iteration, they grow to $P.O$). This suggests that no subsets are removed by Lines~\ref{code:output1-start}-\ref{code:output2-end}. Then, $P.O \subset U_{i+1}$ holds. In summary, $P.O$ does not pruned by simplification, monotonicity and forward closure, therefore $P$ must be returned by SPARE.
%Next, observe that at each iteration $i$, candidates with size $i+2$ are generated. Then, $P.O$'s subset with size $i+2$ are always included in the candidate set at iteration $i$. This indicates that $O' \subset U$, thus any $O'$  would not be pruned by forward closure checking. Since none of the pruning operations removed $O'$, $P$ can be returned by SPARE.
%
%\begin{theorem}[Forward Closure Checking]
%\label{THM:SPM_FCC}
%Let $Lv_i$ be the candidates generated at level $i$ in Algorithm~\ref{algo:apriori_mining},
%if $FC_i$ is a proper pattern, then it is safe to terminate Algorithm~\ref{algo:apriori_mining}
%and directly output $FC_i$.
%\end{theorem}
